### 2017-02-16 doc/manuscript.Rmd
Added models to caption for QIC table

For the confounders, they were chosen based on previous literature, from
directed acyclic graph (DAG) [@Greenland1999a] recommendations, and from
QIC. The DAG recommendations were obtained from using the DAGitty software
[@Textor2011a], http://dagitty.net/. See `r cite_sf('dag_is')` and 
`r cite_sf('dag_bcf')`) for the DAG model. See `r cite_st('qic')` for the
comparison of various models with different covariates using QIC. While the
final GEE model selected as best fitting differed between insulin sensitivity
and beta-cell function measures, the differences in the QIC values were less than 10
between many of the models, suggesting similar fit. As such, we selected the
model that had the fewest covariates and that had similar fit between the
outcome measures. In particular for NEFA, it is used substantially as a source
of fatty acids in hepatic TAG production [@Barrows2006a] and may be a strong
confounder.

@@

>>>>

For the confounders, they were chosen based on previous literature, from
directed acyclic graph (DAG) [@Greenland1999a] recommendations, and from
QIC. The DAG recommendations were obtained from using the DAGitty software
[@Textor2011a], http://dagitty.net/. See `r cite_sf('dag_is')` and 
`r cite_sf('dag_bcf')`) for the DAG model. See `r cite_st('qic')` for the
comparison of various models with different covariates using QIC. While the
final GEE model selected as best fitting differed between insulin sensitivity
and beta-cell function measures, the differences in the QIC values were less than 10
between many of the models, suggesting similar fit. As such, we selected the
model that had the fewest covariates and that had similar fit between the
outcome measures. Total NEFA was included as a confounder because it is used
substantially as a source of fatty acids in hepatic TAG production
[@Barrows2006a].

@@

Given the number of possible combinations of outcome and predictor variables,
only ISI and ISSI-2 with total triacylglycerol fatty acids (nmol/mL) were used to
compare various GEE models and to select a final model.  Baseline age was used
as including both the original age and the time variable would result in
collinearity.  Column names: QIC is the quasi-likelihood information criteria
(smaller values, eg. larger negative values, indicate a better fit compared to
other models), Delta is the QIC minus the lowest QIC (models with delta <10 are 
considered equivalent).  Models were:

- M0: log(ISSI-2) or log(ISI) = total triacylglycerol fatty acids (nmol/mL) + years from baseline
- M1: M0 + fatty acid by time interaction
- M2: M0 + sex + ethnicity + baseline age
- M3: M2 + waist
- M4: M3 + ALT
- M5: M4 + physical activity (MET)
- M6: M5 + total NEFA
- M7: M6 + alcohol intake
- M8: M7 + family history of diabetes
- M9: M8 + smoking status
